A Bias-Variance Decomposition of Information Transfer in Multi-Task Learning

### 2020-08-16 arxiv/proof_main.tex
pf

\paragraph{Step I: Variance reduction.} ........ Consider $\hat M(v)$ for any fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$, 
$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
and 
$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{(\hat a_1 \hat M^{\top}\hat M + \hat a_2\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
with high probability, where $\hat a_1$ and $\hat a_2$ satify \eqref{eq_a2} with $\hat v$ replaced by $v$. Combining them, we get 
\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
\ee 
where $\Delta_{\vari}(v)$ is defined as in \eqref{Deltavarv} but with $\hat v$ replaced by $v$.

\paragraph{Step II: Bounding the bias term.}
Next we use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$. %in \eqref{deltabetapf}.  
%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
\begin{claim}\label{prop_model_shift}
	In the setting of Theorem \ref{thm_model_shift},
	we denote by $K = (v^2X_1^{\top}X_1 + X_2^{\top}X_1)^{-1}$, and
	\begin{align*}
		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_1 - v\beta_2)}^2, \\
		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K \Sigma_2 K \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
	\end{align*}
	Then we have w.h.p.
	\begin{align*}
		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}.
	\end{align*}
%	We have that
%	\begin{align*}
%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
%		\le  \delta_1 - \delta_2
%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
%	\end{align*}
%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
%	\begin{align*}
%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \beta_2)}^2.
%	\end{align*}
\end{claim}

@@

	Denote by $\cE = Z_1^{\top}Z_1 - {n_1}\id$. Then we can write

@@

	Using \eqref{eq_isometric}, we can bound  

>>>>

\paragraph{Step I: Variance reduction.} Consider $\hat M(v)$ for a fixed $v\in \R$. Using Lemma \ref{lem_cov_shift}, we can obtain that for any constant $\e>0$,  
$$  \sigma^2 \cdot \bigtr{(X_2^{\top}X_2)^{-1}\Sigma_2} = \frac{\sigma^2}{\rho_2-1}\left( 1+ \OO(p^{-1/2+e})\right),$$
and 
$$ \sigma^2 \cdot \bigtr{( {v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} \Sigma_2} =   \frac {\sigma^2} {\rho_1 + \rho_2}\cdot \frac1p \bigtr{( a_1(v) \hat M^{\top}\hat M + a_2(v)\id)^{-1}}\left( 1+ \OO(p^{-1/2+e})\right) ,$$
with high probability, where $a_1(v)$ and $a_2(v)$ satify \eqref{eq_a12extra} with $\hat v$ replaced by $v$. The subtraction of these two terms gives 
\be\label{deltavaral-} \delta_{\vari}(v)=\Delta_{\vari}(v) +\OO( \sigma^2 p^{-1/2+e}) \quad \text{w.h.p.},
\ee 
where $\Delta_{\vari}(v)$ is defined as in \eqref{Deltavarv} but with $\hat v$ replaced by $v$.

\paragraph{Step II: Bounding the bias term.}
Next we use \eqref{eq_isometric} to approximate $\delta_{\bias}(v)$ with $\wt\delta_{\bias}(v)$. %in \eqref{deltabetapf}.  
%relate the first term in equation \eqref{eq_te_model_shift} to $\Delta_{\bias}$.
\begin{claim}\label{prop_model_shift}
	In the setting of Lemma \ref{thm_model_shift},
	we denote $K(v) := (v^2X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, and
	\begin{align*}
		%\delta_1 &= v^2 \bignorm{\Sigma_2^{1/2} K X_1^{\top}X_1(\beta_1 - v\beta_2)}^2, \\
		%\delta_2 &= n_1^2\cdot v^2 \bignorm{\Sigma_2^{1/2}K\Sigma_1(\beta_1 - v\beta_2)}, \\
		\delta_{err}(v) := n_1^2 v^2 \bignorm{\Sigma_1^{1/2} K(v) \Sigma_2 K(v) \Sigma_1^{1/2}} \cdot \bignorm{\Sigma_1^{1/2} (\beta_1 - v\beta_2)}^2.
	\end{align*}
	Then we have w.h.p.
	\begin{align*}
		 \left| \delta_{\bias}(v)-\wt\delta_{\bias}(v)\right| 
		\le  \left( \al_+^2(\rho_1)-1 + \OO(p^{-1/2+\e})\right)\delta_{err}(v).
	\end{align*}
%	We have that
%	\begin{align*}
%		-2n_1^2\bigbrace{{2\sqrt{\frac{p}{n_1}}} + {\frac{p}{n_1}}} \delta_3
%		\le  \delta_1 - \delta_2
%		\le n_1^2\bigbrace{2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\bigbrace{2 + 2\sqrt{\frac{p}{n_1}} + \frac{p}{n_1}}\delta_3.
%	\end{align*}
%	For the special case when $\Sigma_1 = \id$ and $\beta_1 - \beta_2$ is i.i.d. with mean $0$ and variance $d^2$, we further have
%	\begin{align*}
%		\bigbrace{1 - \sqrt{\frac{p}{n_1}}}^4 \Delta_{\bias}
%		\le \bignorm{\Sigma_2^{1/2} (X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1(\beta_1 - \beta_2)}^2.
%	\end{align*}
\end{claim}

@@

We can calculate that

@@

	where we denote $\cE: = Z_1^{\top}Z_1 - {n_1}\id$. 
	{\cor(start here)} Using \eqref{eq_isometric}, we can bound  
